<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Bayesian First Aid Tutorial}
-->

Bayesian First Aid Examples
========================================================

This document contains examples of all the `bayes.*` functions implemented in Bayesian First aid including example output from the generic functions `plot`, `summary`, `diagnostics` and `model.code`.

```{r echo=FALSE}
set.seed(123)
```


`binom.test`
------------
A classical binomial test:
```{r}
library(BayesianFirstAid)
binom.test(x=16, n=20)
```
Prepend `binom.test` by `bayes.` to run the Bayesian "version".
```{r}
bayes.binom.test(x=16, n=20)
```
The idea is to respect the arguments to the original `binom.test` as far as possible. For example, setting `p` and `conf.level` as in...

```{r}
binom.test(x=16, n=20, p=0.75, conf.level=0.8)
```
... is respected by `bayes.binom.test`:

```{r}
bayes.binom.test(x=16, n=20, p=0.75, conf.level=0.8)
```

By assigning the result of `bayes.binom.test` to a variable we can get some more useful info by calling `plot` for looking at the posterior (and perhaps a posterior predictive check), `summary` for a more extensive summary than the standard print out above, and `diagnostics` for MCMC diagnostics. The idea is that the behavior of these functions should be consistent for all the `bayes.*.test` functions.  

```{r fig.width=6, fig.height=5, dpi=96}
(fit <- bayes.binom.test(x=16, n=20))
plot(fit)
summary(fit)
diagnostics(fit)
```

Of course, in the case of `bayes.binom.test` the MCMC diagnostics might be a bit silly...

By asking for the `model.code` we get a print out of a script that runs the same analysis as `bayes.binom.test`. This could be copied into an R-script to study how it works or to modify it further.

```{r}
model.code(fit)
```


`t.test`
------------

The alternative for the `t.test` is BEST.

```{r}
x <- rnorm(n=30, mean=2, sd=5)
t.test(x)
```

```{r}
bayes.t.test(x, progress.bar="none")
```

`bayes.t.test` also respects the arguments of the original `t.test`.

```{r}
y <- rnorm(n=30, mean=10, sd=5)
bayes.t.test(x, y, mu=1, conf.level=0.5, progress.bar="none")
```
Or even...

```{r}
# Creating "paired" data
d <- data.frame(x = rnorm(n=30, mean=10, sd=5), group = rep(c("A", "B"), 15))
                
bayes.t.test(x ~ group, paired=T, data=d, progress.bar="none")
```

The same generic functions (`plot`, `summary`, `diagnostics`) works for all fitted models from `bayes.t.test`.

### Output one sample ´bayes.t.test´

```{r  fig.width=6, fig.height=5, dpi=96}
(fit <- bayes.t.test(x, mu=1, progress.bar="none") )
plot(fit)
summary(fit)
diagnostics(fit)
model.code(fit)
```

### Output two sample ´bayes.t.test´

```{r  fig.width=6, fig.height=5, dpi=96}
(fit <- bayes.t.test(x, y, conf.level=0.8, progress.bar="none") )
plot(fit)
summary(fit)
diagnostics(fit)
model.code(fit)
```

### Output paired samples ´bayes.t.test´

```{r  fig.width=6, fig.height=5, dpi=96}
(fit <- bayes.t.test(x ~ group, paired=T, data=d, progress.bar="none"))
plot(fit)
summary(fit)
diagnostics(fit)
model.code(fit)
```

`poisson.test`
------------

```{r}
poisson.test(15, 3, r=3)
```


### Output one sample ´bayes.poisson.test´

```{r  fig.width=6, fig.height=5, dpi=96}
(fit <- bayes.poisson.test(15, 3, r=3))
plot(fit)
summary(fit)
diagnostics(fit)
model.code(fit)
```

### Output two sample ´bayes.poisson.test´

```{r  fig.width=6, fig.height=5, dpi=96}
(fit <- bayes.poisson.test(c(15, 20), c(3, 3), r=1))
plot(fit)
summary(fit)
diagnostics(fit)
model.code(fit)
```

`cor.test`
------------

```{r}
a = c(-1.5, -1.6, -0.5, -1.5, 0.7, 2.1, -1.3, 0.8)
b = c(-1.9, -1.8, -1.5, -0.6, 0.4, 0.7, -1.7, -1.8)
cor.test(a, b, conf.level=0.8)
```

### Output ´bayes.cor.test´

```{r}
(fit <- bayes.cor.test(a, b, conf.level=0.8, progress.bar="none") )
plot(fit)
summary(fit)
diagnostics(fit)
model.code(fit)
```


